Analysis of Odd one out experiment

### 2020-03-18 reports/odd_one_out/analysis_oddoneout.Rmd
oddoneout analysis
closes #3,#4,#5

metrics <- readRDS(file = here("data", "oddoneout", "metrics_190614.rds"))

wrong_trials <- df %>% select(prot_id_version,trial_id,im1:im9) %>% group_by(prot_id_version,trial_id) %>% gather("key", "value",im1:im9) %>% summarize(n = length(unique(value))) %>% filter(n<9) %>% select(-n)

@@

```{r metrics results}
p <- metrics %>% 
  filter(metric!= "ssim_correct" & metric!= "correct") %>% 
  ggplot(aes(x = quintile, y = value_fc7, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme(aspect.ratio = 1) +
  coord_cartesian(ylim = c(0,0.5)) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict CNN")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_explanation_fc7.svg"), p, width = 6, height = 6)

@@

>>>>

metrics <- readRDS(file = here("data", "oddoneout", "metrics_200317.rds"))
metrics_wide <- readRDS(file = here("data", "oddoneout", "metrics_wide_200317.rds"))
wrong_trials <- df %>% select(prot_id_version,trial_id,im1:im9) %>% group_by(prot_id_version,trial_id) %>% gather("key", "value",im1:im9) %>% summarize(n = length(unique(value))) %>% filter(n<9) %>% select(-n)

@@

```{r metrics results}
metrics <- metrics %>% filter(metric!= "ssim_correct")

p <- metrics %>% 
  filter(metric!= "ssim_correct" & metric!= "correct") %>% 
  ggplot(aes(x = quintile, y = value_fc7, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_jitter(0.2)) + 
  theme(aspect.ratio = 1) +
  coord_cartesian(ylim = c(0,0.5)) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict CNN")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_explanation_fc7.svg"), p, width = 6, height = 6)

@@

### Combine metrics

```{r combine metrics}
metrics %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line") + 
  coord_cartesian(ylim = c(0,0.5)) +
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9)

metrics %>%

  ggplot(aes(x = quintile, y = value_partic_top3, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")+
  coord_cartesian(ylim = c(0,0.5)) +
  theme(aspect.ratio = 1)

### Test differences between metrics

```{r test differences between metrics}
x <- metrics %>% filter(!is.infinite(value_partic)) %>% select(value_partic, subject_id,quintile,metric)

x[complete.cases(x),] %>% 
ez::ezANOVA(dv = value_partic, 
              wid = subject_id,
              within=.(quintile,metric))

x <- metrics %>% filter(!is.infinite(value_fc7)) %>% select(value_fc7, subject_id,quintile,metric,category)

x[complete.cases(x),] %>% 
ez::ezANOVA(dv = value_fc7, 
              wid = subject_id,
              within=.(quintile,metric))

## Individual differences

Did some participants showed similar pattern as the cnn?

```{r}
metrics %>% 
  mutate(quintile = as_factor(quintile)) %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")+
  coord_cartesian(ylim = c(0,1)) +
  facet_wrap(~subject_id, ncol = 5)

metrics %>% 
  mutate(quintile = as_factor(quintile)) %>% 
  ggplot(aes(x = quintile, y = value_fc7, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")+
  coord_cartesian(ylim = c(0,1)) +
  facet_wrap(~subject_id, ncol = 5)
